Predicting the Housing Market using \\ Linear Regression

### 2023-10-28 manuscript/Manuscript.tex
created roadmap and added notes

\section{Introduction}

\section{Data}

\section{Methods}

@@

\section{Simulation}

\section{Application}

\section{Discussion and Conclusion}

\section{Appendix}

\section{References}

>>>>

\section{Introduction}
\label{sec:intro}

% Why does it matter?
% What has already been done?
% What is new?

% An overview of the topic
% Existing works
% Why are existing methods not sufficient? What are the elements of an attractive solution?
% Contributions

% A roadmap
The rest of the paper is organized in the following way.
Beginning with the overall introduction located in Section~\ref{sec:intro}.
A brief introduction about the data will be shown in Section~\ref{sec:data}. Here, the variables will be described and explained how they contribute to the research question.
Then, the methodology used in this paper will be explained in Section~\ref{sec:meth}.
Next, the simulation will be reported in Section~\ref{sec:sim}. This section will present the results from the model and have further analysis with tables and figures.
The applications of the results found will be in Section~\ref{sec:app}. More in-depth analysis of how the results can be applied to the real world will be in this section.
Finally, the discussion part for this paper will be in Section~\ref{sec:disc}. The limitations of the current study and future direction will be discussed here.
All the references used in this paper will be included in Section~\ref{sec:refer}.

\section{Data}
\label{sec:data}

% Who collected the data (source)?
% How was the data collected? Sampling frame? Sampling approach?
% What period or range does the data cover?
% Why does the data help answer the research question?
% What exploratory analyses are done (descriptives, visualization, etc.)?

\section{Methods}
\label{sec:meth}

% Establish notation.
% What are the observed data?
% What are the models?
% What are the parameters to be estimated?
% How are the point estimators obtained?
% How are the uncertainty (standard errors) of the point estimators assessed?
% How are the variances of the point estimators estimated?
% How are the null distribution of the testing statistics established?
% Clearly state the assumptions and claims of theoretical results.

@@

\section{Simulation}
\label{sec:sim}

% Aims
% Data generating mechanism
% Estimand/target of analysis
% Methods
% Performance measures

\section{Application}
\label{sec:app}

% Report the statistical analyses in tables/figures.
% When summarizing from tables/figures, paint the big picture, rather than reiterating all of the little details.
% Discussions to link the analyses

\section{Discussion and Conclusion}
\label{sec:disc}

% A summary, again, of the contributions of the research.
% The research question posed as the `need’ of the introduction must be answered here (Zeiger 2000).
% Limitations of the current study
% Future directions.

\section{References}
\label{sec:refer}

% Every reference cited in the paper should appear here.
% References not cited should not appear here.
% All are automatically taken care of by BibTeX.
% Styles are controlled by bib style (.bst file).
